Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-04-03 Documents/M1/realizableFermionicM1/sections/appendix.tex
Some adjustments to paragraph on SSPRK methods.  Added reference to gottlieb at al.

A second-order accurate, strong-stability-preserving explicit Runge-Kutta scheme, referred as SSPRK2, has the following non-zero components:
\begin{align}
  \tilde{a}_{21} &= 1, \nonumber \\
  \tilde{w}_{1} &= 1/2, \quad \tilde{w}_{2} = 1/2. \nonumber 
\end{align}
A third-order accurate, strong-stability-preserving explicit Runge-Kutta scheme, was referred as SSPRK3.
It has the following non-zero components:
\begin{align}
  \tilde{a}_{21} &= 1, \nonumber \\
  \tilde{a}_{31} &= 1/4, \quad \tilde{a}_{32} = 1/4, \nonumber \\
  \tilde{w}_{1} &= 1/6, \quad \tilde{w}_{2} = 1/6, \quad \tilde{w}_{3} =2/3 \nonumber
\end{align}

>>>>

To compare the performance of the IMEX schemes in the streaming limit (no collisions), we also compute results with explicit strong stability-preserving Runge-Kutta methods \cite{gottlieb_etal_2001}.  
(All elements of the implicit Butcher tableau are zero.)  
The optimal second-order accurate, strong-stability-preserving Runge-Kutta scheme (SSPRK2) has the following non-zero components
\begin{align}
  \tilde{a}_{21} &= 1, \nonumber \\
  \tilde{w}_{1} &= 1/2, \quad \tilde{w}_{2} = 1/2. \nonumber 
\end{align}
The optimal third-order accurate, strong-stability-preserving Runge-Kutta scheme (SSPRK3) has the following non-zero components
\begin{align}
  \tilde{a}_{21} &= 1, \nonumber \\
  \tilde{a}_{31} &= 1/4, \quad \tilde{a}_{32} = 1/4, \nonumber \\
  \tilde{w}_{1} &= 1/6, \quad \tilde{w}_{2} = 1/6, \quad \tilde{w}_{3} =2/3. \nonumber
\end{align}
